Wavelet Multiresolution Spatio-Temporal Modelling Using the Integro-Difference Equation

### 2011-02-15 Multiresolution_framework/ltx/manuscript.tex
edits to MRA section

 % TO DELETE
\newcommand{\mike}[1]{\textsf{\emph{\textbf{\textcolor{red}{#1}}}}} 
\newcommand{\dean}[1]{\textsf{\emph{\textbf{\textcolor{green}{#1}}}}} 
\newcommand{\parham}[1]{\textsf{\emph{\textbf{\textcolor{blue}{#1}}}}} 
\newcommand{\ken}[1]{\textsf{\emph{\textbf{\textcolor{magenta}{#1}}}}} 
%    \documentclass[journal,a4paper]{IEEEtran}
     \documentclass[10pt,twocolumn,twoside]{IEEEtran}
%     \documentclass[11pt,draftcls,onecolumn,peerreview]{IEEEtran} 
%         \topmargin       -6.0mm
%          \oddsidemargin      0mm
%          \evensidemargin     0mm
%          \textheight     223.5mm
%         \textwidth      170.0mm

@@

Assuming $v_t(.)$ and $w(.)$ are square-integrable functions, MRA of the one-dimensional IDE can be obtained by expanding  both the field and the kernel in the equation (\ref{DiscreteTimeModel}) in terms of the translations and dilations of a scaling function $\phi(s)$ and a mother wavelet $\psi(s)$. For the one-dimensional kernel this is given by,

@@

>>>>

 % TO DELETE

    \documentclass[journal,a4paper]{IEEEtran}
 %    \documentclass[10pt,twocolumn,twoside]{IEEEtran}
%     \documentclass[11pt,draftcls,onecolumn,peerreview]{IEEEtran} 
%         \topmargin       -6.0mm
%          \oddsidemargin      0mm
%          \evensidemargin     0mm
%          \textheight     223.5mm
%         \textwidth      170.0mm

\usepackage{color}
\newcommand{\mike}[1]{\textsf{\emph{\textbf{\textcolor{red}{#1}}}}} 
\newcommand{\dean}[1]{\textsf{\emph{\textbf{\textcolor{green}{#1}}}}} 
\newcommand{\parham}[1]{\textsf{\emph{\textbf{\textcolor{blue}{#1}}}}} 
\newcommand{\ken}[1]{\textsf{\emph{\textbf{\textcolor{magenta}{#1}}}}}

@@

Assuming $v_t(.)$ and $w(.)$ are square-integrable functions, MRA of the one-dimensional IDE can be obtained by expanding  both the field and the kernel in the equation (\ref{DiscreteTimeModel}) in terms of the translations and dilations of a scaling function $\phi(r)$ and a mother wavelet $\psi(r)$. For the one-dimensional kernel this is given by,

@@

\parham{Mike you can add state-space derivation using Galerkin projection here.}
